A large-scale analysis of racial disparities in police stops across the United

### 2019-12-10 lib/paper_results.Rmd
scaling factor

```{r search_rates}
tbl <- pfs$rates$search %>% 
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(
    average_n = mean(n),
    average_n_searches = mean(n_searches),
    average_search_rate = mean(search_rate),
    std_error = sqrt(
      average_search_rate * (1 - average_search_rate) / average_n
    ),
    CI_radius = 1.96 * std_error,
    CI_lower = average_search_rate - CI_radius,
    CI_upper = average_search_rate + CI_radius
  ) %>%
  ungroup()
tbl %>% kable()
prop_tbl <- tbl %>%
  mutate(
    n_success = average_n_searches,
    n_failure = average_n - average_n_searches
  )
```

p-values:

@@

```{r disparity-thresholds-tables}
kable(disp$city$threshold$results$aggregate_thresholds)
kable(disp$state$threshold$results$aggregate_thresholds)
```

```{r disparity-city-thresholds-plot, fig.height=5, fig.width=10}
axis_min <- max(
  min(
    disp$city$threshold$plots$aggregate$data$minority_rate,
    disp$city$threshold$plots$aggregate$data$majority_rate
  ) - 0.05, 0
)
axis_max <- min(
  max(
    disp$city$threshold$plots$aggregate$data$minority_rate,
    disp$city$threshold$plots$aggregate$data$majority_rate
  ) + 0.05, 1
)
disp$city$threshold$plots$aggregate + 
  theme(legend.position = "none", plot.title = element_blank()) + 
  scale_x_continuous(
    limits = c(axis_min, axis_max), breaks = seq(0, .5, 0.05),
    labels = scales::percent_format(accuracy = 1), expand = c(0,0)
  ) + 
  scale_y_continuous(
    limits = c(axis_min, axis_max), breaks = seq(0, .5, 0.05),
    labels = scales::percent_format(accuracy = 1),expand = c(0,0)
  ) 
```

```{r disparity-state-thresholds-plot, fig.height=5, fig.width=10}
disp$state$threshold$plots$aggregate + theme(legend.position = "none")
```

```{r disparity-city-ppc-search, fig.height=5, fig.width=8}
disp$city$threshold$ppc$search_rate
```

```{r disparity-city-ppc-hit, fig.height=5, fig.width=8}
disp$city$threshold$ppc$hit_rate
```

```{r disparity-state-ppc-search, fig.height=5, fig.width=8}
disp$state$threshold$ppc$search_rate
```

```{r disparity-state-ppc-hit, fig.height=5, fig.width=8}
disp$state$threshold$ppc$hit_rate
```

>>>>

```{r search_rates}
tbl <- pfs$rates$search %>% 
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(
    average_n = mean(n),
    average_n_searches = mean(n_searches),
    average_search_rate = mean(search_rate),
    std_error = sqrt(
      average_search_rate * (1 - average_search_rate) / average_n
    ),
    CI_radius = 1.96 * std_error,
    CI_lower = average_search_rate - CI_radius,
    CI_upper = average_search_rate + CI_radius
  ) %>%
  ungroup()
tbl %>% kable()
ptbl <- tbl %>%
  mutate(
    n_success = average_n_searches,
    n_failure = average_n - average_n_searches
  )
pstate <- filter(pbl, str_detect(agency, 'state'))
pcity <- filter(pbl, str_detect(agency, 'municipal'))
```

State search p-values:
`r slice(pstate, 1:2) %>% select(subject_race) %>% kable()`:
`r slice(pstate, 1:2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`

`r slice(ptbl, -2) %>% select(agency, subject_race) %>% kable()`:
`r slice(ptbl, -2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`

`r slice(ptbl, 2:3) %>% select(agency, subject_race) %>% kable()`:
`r slice(ptbl, 2:3) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`

`r slice(ptbl, 4:5) %>% select(agency, subject_race) %>% kable()`:
`r slice(ptbl, 4:5) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`

`r slice(ptbl, ) %>% select(agency, subject_race) %>% kable()`:
`r slice(ptbl, -5) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`

`r slice(ptbl, 5:6) %>% select(agency, subject_race) %>% kable()`:
`r slice(ptbl, 5:6) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`

@@

Scaling priors by 0.5x:
```{r disparity-thresholds-tables-0.5}
kable(disp$city$threshold$prior_scaling_factor_0.5$results$aggregate_thresholds)
kable(disp$state$threshold$prior_scaling_factor_0.5$results$aggregate_thresholds)
```

Priors at 1.0 (normal):
```{r disparity-thresholds-tables-1.0}
kable(disp$city$threshold$prior_scaling_factor_1$results$aggregate_thresholds)
kable(disp$state$threshold$prior_scaling_factor_1$results$aggregate_thresholds)
```

Scaling priors by 1.5x:
```{r disparity-thresholds-tables-1.5}
kable(disp$city$threshold$prior_scaling_factor_1.5$results$aggregate_thresholds)
kable(disp$state$threshold$prior_scaling_factor_1.5$results$aggregate_thresholds)
```

\newpage
Threshold plot for normal priors:

```{r disparity-city-thresholds-plot, fig.height=5, fig.width=10}
axis_min <- max(
  min(
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$minority_rate,
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$majority_rate
  ) - 0.05, 0
)
axis_max <- min(
  max(
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$minority_rate,
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$majority_rate
  ) + 0.05, 1
)
disp$city$threshold$prior_scaling_factor_1$plots$aggregate + 
  theme(legend.position = "none", plot.title = element_blank()) + 
  scale_x_continuous(
    limits = c(axis_min, axis_max), breaks = seq(0, .5, 0.05),
    labels = scales::percent_format(accuracy = 1), expand = c(0,0)
  ) + 
  scale_y_continuous(
    limits = c(axis_min, axis_max), breaks = seq(0, .5, 0.05),
    labels = scales::percent_format(accuracy = 1),expand = c(0,0)
  ) 
```

\newpage
Normal priors:

```{r disparity-state-thresholds-plot, fig.height=5, fig.width=10}
disp$state$threshold$prior_scaling_factor_1$plots$aggregate + theme(legend.position = "none")
```

\newpage
Normal priors:

```{r disparity-city-ppc-search, fig.height=5, fig.width=8}
disp$city$threshold$prior_scaling_factor_1$ppc$search_rate
```

\newpage
Normal priors:

```{r disparity-city-ppc-hit, fig.height=5, fig.width=8}
disp$city$threshold$prior_scaling_factor_1$ppc$hit_rate
```

\newpage
Normal priors:

```{r disparity-state-ppc-search, fig.height=5, fig.width=8}
disp$state$threshold$prior_scaling_factor_1$ppc$search_rate
```

\newpage
Normal priors:

```{r disparity-state-ppc-hit, fig.height=5, fig.width=8}
disp$state$threshold$prior_scaling_factor_1$ppc$hit_rate
```
